## Script for Network augmented SW-CRT fixed-effects and GEE analysis when network is fixed at baseline ##
## Carly's backbone script with James model specification ##

---
title: "Publication Facing Script"
output: html_notebook
---

## Load our libraries

```{r}
#install.packages("broom.mixed",repos=NULL,contriburl="file:/opt/software/cran/src/contrib")
library(lme4)
library(nlme)
library(Gmisc)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(broom.mixed)
library(geepack)
```

Setting glmer options:

```{r}
#options(lme4.control=glmerControl(optimizer="nloptwrap",calc.derivs = F)) #Carly
options(lme4.control=glmerControl(optimizer="bobyqa",tolPwrss=1e-7,optCtrl=list(maxfun=1e5))) #James
```

#Optimization settings to avoidmitigate convergence warnings:
#mod_spill <- glmer("model",family=binomial(link="logit"),data=data, nAGQ=2, #control=glmerControl(optimizer="bobyqa",tolPwrss=1e-7,optCtrl=list(maxfun=1e5)))

## Load in the Data

```{r}
#set some new pathways
outdir<-"/drives/drive1/54054dua/idata/cbobak/"
outdir_spillover<-paste(outdir,"spillover_analysis/",sep="")
data<-read.csv(paste(outdir_spillover,"acp_data_with_spill_strict_prior_stochastic.csv",sep=""))
data$chosp_step <- as.factor(data$hosp_step)
data$ctrialmonth <- as.factor(data$trialmonth)
data$cbregion <- as.factor(data$bregion)
data$cageg <- as.factor(data$ageg)
data$ccovid_status <- as.factor(data$covid_status)
data$ccharl_sc <- as.factor(data$charl_sc)
data$csq <- as.factor(data$sq)
data$gameTime<-data$total_game_time
#So that effect-size corresponds to 10 percentage-points, multiply the following by 10
data$physWPost_strict <- (10/8)*data$physWPost_tinv #8 = max internal physicians encountered. Standardize this way to get similarly-sized estimates to those for phase. However, its max value is < 1 = max(physWPost_strict_ext_tinv) because we divide by the total number of intervened physicians and the internal peers were not intervened on until the same step as the focal physician.
data$physWPost_strict_ext <- 10*data$physWPost_strict_ext_tinv
```

#Carly's data and output transforming functions:

For nicer output:

```{r, include=FALSE}
variable_mapping <- list(
  #"(Intercept)" = "Baseline",
  "gameTime" = "Game Time",
  "chosp_step2" = "Step of the trial (Two)",
  "chosp_step3" = "Step of the trial (Three)",
  "chosp_step4" = "Step of the trial (Four)",
  "chosp_step5" = "Step of the trial (Five)",
  "n_intervened_mds" = "Number of Intervened Physicians Associated with Stay",
  "n_stay_mds" = "Number of Physicians Associated with Stay",
  "physWPost" = "Physician Spillover",
  "ctrialmonth2" = "Month of the Trial (Two)",
  "ctrialmonth3" = "Month of the Trial (Three)",
  "ctrialmonth4" = "Month of the Trial (Four)",
  "ctrialmonth5" = "Month of the Trial (Five)",
  "ctrialmonth6" = "Month of the Trial (Six)",
  "ctrialmonth7" = "Month of the Trial (Seven)",
  "ctrialmonth8" = "Month of the Trial (Eight)",
  "ctrialmonth9" = "Month of the Trial (Nine)",
  "ctrialmonth10" = "Month of the Trial (Ten)",
  "ctrialmonth11" = "Month of the Trial (Eleven)",
  "ctrialday" = "Trial Day",
  "cbregionsouth" = "Region (South)",
  "cbregionwest" = "Region (West)",
  "cageg75" = "Patient age (75–84 years)",
  "cageg85" = "Patient age (≥ 85 years)",
  "ccovid_statusYes" = "Covid status (Covid positive)",
  "cad_cd" = "Coronary artery disease",
  "dem_cd" = "Dementia",
  "heart_cd" = "Heart failure",
  "diab_cd" = "Diabetes",
  "lung_cd" = "COPD",
  "ccharl_sc1" = "Charlson score (One)",
  "ccharl_sc2" = "Charlson score (Two)",
  "ccharl_sc3" = "Charlson score (Three)",
  "ccharl_sc4" = "Charlson score (Four)",
  "ccharl_sc5" = "Charlson score (Five)",
  "n_w2mds" = "Practice size",
  "covid_stays" = "Proportion of hospitalizations with COVID",
  "Q2_Y20_Adj_ACP" = "ACP rate in Quarter 2 of 2020 (effect of a 10 percentage-point increase)",
  "Delta_ACP" = "Change in ACP rate between Q2 of 2019 and Q1 of 2020",
  "csqY" = "Would you be surprised if the patient died in the next year (Yes)",
  "phase" = "Intervention",
  "scaled_days_since_intervention" = "Day since hospital intervention"
)

reorder_by_priority<-function(df,priority_vars){
  for(var in rev(priority_vars)){
    if(var %in% df$Term){
      priority_row <- which(df$Term==var)
      df<-rbind(df[priority_row,],df[-priority_row,])
    }
  }
  return(df)
}

format_model_output_logistic <- function(model, variable_mapping) {
  # Exponentiate estimates for odds ratios
  tidy_model <- broom.mixed::tidy(model) %>%
    mutate(estimate = exp(estimate))

  # Dynamically replace term components based on mapping
  tidy_model$term <- sapply(tidy_model$term, function(term) {
    components <- unlist(strsplit(term, ":"))
    mapped_components <- sapply(components, function(component) {
      if (component %in% names(variable_mapping)) {
        return(variable_mapping[[component]])
      } else {
        return(component)
      }
    })
    return(paste(mapped_components, collapse = " x "))
  })
  
  # Calculate and exponentiate 95% CI for odds ratios
  ci <- exp(confint(model, method="Wald", level=0.95))
  ci_df <- as.data.frame(ci)
  names(ci_df) <- c("lower_ci", "upper_ci")
  ci_df$term<-sapply(row.names(ci_df), function(term) {
    components <- unlist(strsplit(term, ":"))
    mapped_components <- sapply(components, function(component) {
      if (component %in% names(variable_mapping)) {
        return(variable_mapping[[component]])
      } else {
        return(component)
      }
    })
    return(paste(mapped_components, collapse = " x "))
  })
  
  # Merge tidy model output with CIs
  tidy_model <- left_join(tidy_model,ci_df)
  
  # Include formatted output with Odds Ratios, CIs, and p-values
  tidy_model <- tidy_model %>%
    mutate(formatted_p = ifelse(p.value>=0.001,round(p.value,3),"<0.001"),
      formatted_output = paste0(round(estimate, 3),
                                     " (", round(lower_ci, 3), ", ", round(upper_ci, 3), ")"))
  
  # Define priority variables and their interactions
  priority_vars <- c("(Intercept)","Intervention", "Game Time", "Number of Intervened Physicians Associated with Stay",
                     "Number of Physicians Associated with Stay","Physician Spillover", "Day since hospital intervention","retention","Step of the trial", "Proportion of hospitalizations with COVID")
  
  tidy_model$Term <- tidy_model$term
  tidy_model<-reorder_by_priority(tidy_model,priority_vars = priority_vars)
  
  # Select and rename columns for publication
  tidy_model <- tidy_model %>%
    select(Term = term, Formatted = formatted_output, P_Value_Formatted = formatted_p)
  
  return(tidy_model)
}

```

We've constructed a variable called `day_since_intervention` which is the `trial_day` variable - `intervention_day` (taken as the minimum day where `phase==1` for each hospital) if `day_since_intervention`>0; and 0 otherwise. Note, each stay here is assigned a 'trial day' despite stays operating over many days. I'll need to check with Megan to confirm how this assignment occurred so we can be away of any limitations. 

```{r}
plot(data$day_since_intervention,data$trialday)
```

If we run our model with `day_since_intervention` as is, we get two warnings.

1. fixed-effect model matrix is rank deficient so dropping 1 column / coefficient
2. Warning: Some predictor variables are on very different scales: consider rescaling

It ends up dropping the interaction term of `phase` and `day_since_intervention`.


I'm going to suggest, for now, we redefine a scaled version of this variable:

```{r}
# scaling and rank deficient issue continued
data$scaled_days_since_intervention<-ifelse(data$day_since_intervention>0,log1p(data$day_since_intervention),0)
```

which now looks like:

```{r}
hist(data$scaled_days_since_intervention)
```


Our hypothesis is that spillover effects may shift as we get further from intervention, and social connections reinforcing the intervention may modify the decay of the intervention influence. 


We can hard code in an $post \time retention$ and $expose \times post \time retention$ variables:

```{r}
data$phaseret <- data$phase*data$day_since_intervention/90
data$phaseexpret <- data$phase*data$physWPost_strict_ext*data$day_since_intervention/90
data$n_intret <- data$n_intervened_mds*data$day_since_intervention/90
data$n_intexpret <- data$n_intervened_mds*data$physWPost_strict*data$day_since_intervention/90
hist(data$phaseret)
```

## Fixed-effect and GEE models with time-invariant network estimated in paper (Do not include n_stay_mds in the phase models) ##

```{r}
mod_phase <- glm(acp~phase+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+factor(HospitalID),family=binomial(link="logit"),data=data)

mod_phase_gee <- geeglm(acp~phase+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq,family=binomial(link="logit"),id=HospitalID,corstr='exchangeable',data=data)

mod_phasespill <- glm(acp~phase+physWPost_strict_ext+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+factor(HospitalID),family=binomial(link="logit"),data=data)

mod_phasespill_gee <- geeglm(acp~phase+physWPost_strict_ext+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq,family=binomial(link="logit"),id=HospitalID,corstr='exchangeable',data=data)

mod_phasespillint <- glm(acp~phase*physWPost_strict_ext+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+factor(HospitalID),family=binomial(link="logit"),data=data)

mod_phasespillint_gee <- geeglm(acp~phase*physWPost_strict_ext+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq,family=binomial(link="logit"),id=HospitalID,corstr='exchangeable',data=data)

mod_phasespillintret <- glm(acp~phase*physWPost_strict_ext+phaseret+phaseexpret+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+factor(HospitalID),family=binomial(link="logit"),data=data)

mod_phasespillintret_gee <- geeglm(acp~phase*physWPost_strict_ext+phaseret+phaseexpret+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq,family=binomial(link="logit"),id=HospitalID,corstr='exchangeable',data=data)

mod_dose <- glm(acp~n_intervened_mds+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+factor(HospitalID),family=binomial(link="logit"),data=data)

mod_dose_gee <- geeglm(acp~n_intervened_mds+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq,family=binomial(link="logit"),id=HospitalID,corstr='exchangeable',data=data)

mod_dosespill <- glm(acp~n_intervened_mds+physWPost_strict+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+factor(HospitalID),family=binomial(link="logit"),data=data)

mod_dosespill_gee <- geeglm(acp~n_intervened_mds+physWPost_strict+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq,family=binomial(link="logit"),id=HospitalID,corstr='exchangeable',data=data)

mod_dosespillint <- glm(acp~n_intervened_mds*physWPost_strict+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+factor(HospitalID),family=binomial(link="logit"),data=data)

mod_dosespillint_gee <- geeglm(acp~n_intervened_mds*physWPost_strict+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq,family=binomial(link="logit"),id=HospitalID,corstr='exchangeable',data=data)

mod_dosespillintret <- glm(acp~n_intervened_mds*physWPost_strict+n_intret+n_intexpret+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+factor(HospitalID),family=binomial(link="logit"),data=data)

mod_dosespillintret_gee <- geeglm(acp~n_intervened_mds*physWPost_strict+n_intret+n_intexpret+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq,family=binomial(link="logit"),id=HospitalID,corstr='exchangeable',data=data)

#Output results of fixed-effect analyses
mod_phase_res<-format_model_output_logistic(mod_phase,variable_mapping = variable_mapping)
write.csv(mod_phase_res,"causal_spillover_phase_tinv_fe.csv",row.names=F)

mod_phasespill_res<-format_model_output_logistic(mod_phasespill,variable_mapping = variable_mapping)
write.csv(mod_phasespill_res,"causal_spillover_phasespill_tinv_fe.csv",row.names=F)

mod_phasespillint_res<-format_model_output_logistic(mod_phasespillint,variable_mapping = variable_mapping)
write.csv(mod_phasespillint_res,"causal_spillover_phasespillint_tinv_fe.csv",row.names=F)

mod_phasespillintret_res<-format_model_output_logistic(mod_phasespillintret,variable_mapping = variable_mapping)
write.csv(mod_phasespillintret_res,"causal_spillover_phasespillintret_tinv_fe.csv",row.names=F)

mod_dose_res<-format_model_output_logistic(mod_dose,variable_mapping = variable_mapping)
write.csv(mod_dose_res,"causal_spillover_dose_tinv_fe.csv",row.names=F)

mod_dosespill_res<-format_model_output_logistic(mod_dosespill,variable_mapping = variable_mapping)
write.csv(mod_dosespill_res,"causal_spillover_dosespill_tinv_fe.csv",row.names=F)

mod_dosespillint_res<-format_model_output_logistic(mod_dosespillint,variable_mapping = variable_mapping)
write.csv(mod_dosespillint_res,"causal_spillover_dosespillint_tinv_fe.csv",row.names=F)

mod_dosespillintret_res<-format_model_output_logistic(mod_dosespillintret,variable_mapping = variable_mapping)
write.csv(mod_dosespillintret_res,"causal_spillover_dosespillintret_tinv_fe.csv",row.names=F)

#Output results of GEE analyses
sink(file="causal_spillover_tinv_gee.txt")
summary(mod_phase_gee)
summary(mod_phasespill_gee)
summary(mod_phasespillint_gee)
summary(mod_phasespillintret_gee) 
summary(mod_dose_gee)
summary(mod_dosespill_gee)
summary(mod_dosespillint_gee)
summary(mod_dosespillintret_gee)
sink()

```

