## Script for Network augmented SW-CRT mixed-effect model and causal estimates based on potential outcomes ##
##  when network is fixed at baseline ##
## Carly's backbone script with James model specification 4/15/2026 ##

---
title: "Publication Facing Script"
output: html_notebook
---

## Load our libraries

```{r}
#install.packages("broom.mixed",repos=NULL,contriburl="file:/opt/software/cran/src/contrib")
library(lme4)
library(nlme)
library(Gmisc)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(broom.mixed)
```

Setting glmer options:

```{r}
#options(lme4.control=glmerControl(optimizer="nloptwrap",calc.derivs = F)) #Carly
options(lme4.control=glmerControl(optimizer="bobyqa",tolPwrss=1e-7,optCtrl=list(maxfun=1e5))) #James
```

#Optimization settings to avoid or mitigate convergence warnings:
#mod_spill <- glmer("model",family=binomial(link="logit"),data=data, nAGQ=2, #control=glmerControl(optimizer="bobyqa",tolPwrss=1e-7,optCtrl=list(maxfun=1e5)))

## Load in the Data

```{r}
#set some new pathways
outdir<-"/drives/drive1/54054dua/idata/cbobak/"
outdir_spillover<-paste(outdir,"spillover_analysis/",sep="")
data<-read.csv(paste(outdir_spillover,"acp_data_with_spill_strict_prior_stochastic.csv",sep=""))
data$chosp_step <- as.factor(data$hosp_step)
data$ctrialmonth <- as.factor(data$trialmonth)
data$cbregion <- as.factor(data$bregion)
data$cageg <- as.factor(data$ageg)
data$ccovid_status <- as.factor(data$covid_status)
data$ccharl_sc <- as.factor(data$charl_sc)
data$csq <- as.factor(data$sq)
data$gameTime<-data$total_game_time
#So that effect-size corresponds to 10 percentage-points, multiply the following by 10
data$physWPost_strict <- (10/8)*data$physWPost_tinv #8 = max internal physicians encountered. Standardize this way to get similarly-sized estimates to those for phase. However, its max value is < 1 = max(physWPost_strict_ext_tinv) because we divide by the total number of intervened physicians and the internal peers were not intervened on until the same step as the focal physician.
data$physWPost_strict_ext <- 10*data$physWPost_strict_ext_tinv #Unit change of 0.1 approximates mean(physWPost_strict_ext_tinv)
```

#Carly's data and output transforming functions:

For nicer output:

```{r, include=FALSE}
variable_mapping <- list(
  #"(Intercept)" = "Baseline",
  "gameTime" = "Game Time",
  "chosp_step2" = "Step of the trial (Two)",
  "chosp_step3" = "Step of the trial (Three)",
  "chosp_step4" = "Step of the trial (Four)",
  "chosp_step5" = "Step of the trial (Five)",
  "n_intervened_mds" = "Number of Intervened Physicians Associated with Stay",
  "n_stay_mds" = "Number of Physicians Associated with Stay",
  "physWPost" = "Physician Spillover",
  "ctrialmonth2" = "Month of the Trial (Two)",
  "ctrialmonth3" = "Month of the Trial (Three)",
  "ctrialmonth4" = "Month of the Trial (Four)",
  "ctrialmonth5" = "Month of the Trial (Five)",
  "ctrialmonth6" = "Month of the Trial (Six)",
  "ctrialmonth7" = "Month of the Trial (Seven)",
  "ctrialmonth8" = "Month of the Trial (Eight)",
  "ctrialmonth9" = "Month of the Trial (Nine)",
  "ctrialmonth10" = "Month of the Trial (Ten)",
  "ctrialmonth11" = "Month of the Trial (Eleven)",
  "ctrialday" = "Trial Day",
  "cbregionsouth" = "Region (South)",
  "cbregionwest" = "Region (West)",
  "cageg75" = "Patient age (75–84 years)",
  "cageg85" = "Patient age (≥ 85 years)",
  "ccovid_statusYes" = "Covid status (Covid positive)",
  "cad_cd" = "Coronary artery disease",
  "dem_cd" = "Dementia",
  "heart_cd" = "Heart failure",
  "diab_cd" = "Diabetes",
  "lung_cd" = "COPD",
  "ccharl_sc1" = "Charlson score (One)",
  "ccharl_sc2" = "Charlson score (Two)",
  "ccharl_sc3" = "Charlson score (Three)",
  "ccharl_sc4" = "Charlson score (Four)",
  "ccharl_sc5" = "Charlson score (Five)",
  "n_w2mds" = "Practice size",
  "covid_stays" = "Proportion of hospitalizations with COVID",
  "Q2_Y20_Adj_ACP" = "ACP rate in Quarter 2 of 2020 (effect of a 10 percentage-point increase)",
  "Delta_ACP" = "Change in ACP rate between Q2 of 2019 and Q1 of 2020",
  "csqY" = "Would you be surprised if the patient died in the next year (Yes)",
  "phase" = "Intervention",
  "scaled_days_since_intervention" = "Day since hospital intervention"
)

reorder_by_priority<-function(df,priority_vars){
  for(var in rev(priority_vars)){
    if(var %in% df$Term){
      priority_row <- which(df$Term==var)
      df<-rbind(df[priority_row,],df[-priority_row,])
    }
  }
  return(df)
}

format_model_output_logistic <- function(model, variable_mapping) {
  # Exponentiate estimates for odds ratios
  tidy_model <- broom.mixed::tidy(model) %>%
    mutate(estimate = exp(estimate))

  # Dynamically replace term components based on mapping
  tidy_model$term <- sapply(tidy_model$term, function(term) {
    components <- unlist(strsplit(term, ":"))
    mapped_components <- sapply(components, function(component) {
      if (component %in% names(variable_mapping)) {
        return(variable_mapping[[component]])
      } else {
        return(component)
      }
    })
    return(paste(mapped_components, collapse = " x "))
  })
  
  # Calculate and exponentiate 95% CI for odds ratios
  ci <- exp(confint(model, method="Wald", level=0.95))
  ci_df <- as.data.frame(ci)
  names(ci_df) <- c("lower_ci", "upper_ci")
  ci_df$term<-sapply(row.names(ci_df), function(term) {
    components <- unlist(strsplit(term, ":"))
    mapped_components <- sapply(components, function(component) {
      if (component %in% names(variable_mapping)) {
        return(variable_mapping[[component]])
      } else {
        return(component)
      }
    })
    return(paste(mapped_components, collapse = " x "))
  })
  
  # Merge tidy model output with CIs
  tidy_model <- left_join(tidy_model,ci_df)
  
  # Include formatted output with Odds Ratios, CIs, and p-values
  tidy_model <- tidy_model %>%
    mutate(formatted_p = ifelse(p.value>=0.001,round(p.value,3),"<0.001"),
      formatted_output = paste0(round(estimate, 3),
                                     " (", round(lower_ci, 3), ", ", round(upper_ci, 3), ")"))
  
  # Define priority variables and their interactions
  priority_vars <- c("(Intercept)","Intervention", "Game Time", "Number of Intervened Physicians Associated with Stay",
                     "Number of Physicians Associated with Stay","Physician Spillover", "Day since hospital intervention","retention","Step of the trial", "Proportion of hospitalizations with COVID")
  
  tidy_model$Term <- tidy_model$term
  tidy_model<-reorder_by_priority(tidy_model,priority_vars = priority_vars)
  
  # Select and rename columns for publication
  tidy_model <- tidy_model %>%
    select(Term = term, Formatted = formatted_output, P_Value_Formatted = formatted_p)
  
  return(tidy_model)
}

```

We've constructed a variable called `day_since_intervention` which is the `trial_day` variable - `intervention_day` (taken as the minimum day where `phase==1` for each hospital) if `day_since_intervention`>0; and 0 otherwise. Note, each stay here is assigned a 'trial day' despite stays operating over many days. I'll need to check with Megan to confirm how this assignment occurred so we can be away of any limitations. 

```{r}
plot(data$day_since_intervention,data$trialday)
```

If we run our model with `day_since_intervention` as is, we get two warnings.

1. fixed-effect model matrix is rank deficient so dropping 1 column / coefficient
2. Warning: Some predictor variables are on very different scales: consider rescaling

It ends up dropping the interaction term of `phase` and `day_since_intervention`.


I'm going to suggest, for now, we redefine a scaled version of this variable:

```{r}
# scaling and rank deficient issue continued
data$scaled_days_since_intervention<-ifelse(data$day_since_intervention>0,log1p(data$day_since_intervention),0)

#also fails
#data$scaled_days_since_intervention<-ifelse(data$day_since_intervention>0,log(data$day_since_intervention),0)

# try rescaling:
#data$scaled_days_since_intervention<-ifelse(data$day_since_intervention>0,data$day_since_intervention/7,0)
```

which now looks like:

```{r}
hist(data$scaled_days_since_intervention)
```


Our hypothesis is that spillover effects may shift as we get further from intervention, and social connections reinforcing the intervention may modify the decay of the intervention influence. 


We can hard code in an $post \time retention$ and $expose \times post \time retention$ variables:

```{r}
data$phaseret <- data$phase*data$day_since_intervention/90
data$phaseexpret <- data$phase*data$physWPost_strict_ext*data$day_since_intervention/90
data$n_intret <- data$n_intervened_mds*data$day_since_intervention/90
data$n_intexpret <- data$n_intervened_mds*data$physWPost_strict*data$day_since_intervention/90
hist(data$phaseret)
```

## Data setup and functions for potential outcomes evaluation (Do not include n_stay_mds in the phase models) ##

```{r}
#Expand predictors for step, trial_month, region, charlson score and the surprise question (csq)
factstep <- cbind(1*(data$chosp_step==2),1*(data$chosp_step==3),1*(data$chosp_step==4),1*(data$chosp_step==5))
factmonth <- cbind(1*(data$ctrialmonth==2),1*(data$ctrialmonth==3),1*(data$ctrialmonth==4),1*(data$ctrialmonth==5),1*(data$ctrialmonth==6),1*(data$ctrialmonth==7),1*(data$ctrialmonth==8),1*(data$ctrialmonth==9),1*(data$ctrialmonth==10),1*(data$ctrialmonth==11))
factregion <- cbind(1*(data$cbregion=='south'),1*(data$cbregion=='west'))
factage <- cbind(1*(data$cageg==75),1*(data$cageg==85))
factcovid <- 1*(data$ccovid_status=='Yes')
factccharl <- cbind(1*(data$ccharl_sc==1),1*(data$ccharl_sc==2),1*(data$ccharl_sc==3),1*(data$ccharl_sc==4),1*(data$ccharl_sc==5))
factcsq <- 1*(data$csq=='Y')
factintercept <- rep(1,nrow(data))
datacov <- data.frame(factintercept,data$phase,factstep,factmonth,data$ctrialday,factregion,factage,factcovid,data[,c("cad_cd","dem_cd","heart_cd","diab_cd","lung_cd")],factccharl,data[,c("n_w2mds","covid_stays","Q2_Y20_Adj_ACP","Delta_ACP")],factcsq)
names(datacov) <- c("intercept","phase",paste("chosp_step",2:5,sep=""),paste("ctrialmonth",2:11,sep=""),"ctrialday",paste("cbregion",c("south","west"),sep=""),paste("age",c(75,85),sep=""),"ccovid_status","cad_cd","dem_cd","heart_cd","diab_cd","lung_cd",paste("ccharl_sc",1:5,sep=""),"n_w2mds","covid_stays","Q2_Y20_Adj_ACP","Delta_ACP","csq")

#Function when a single variable is manipulated
estpotout <- function(X1,X0,coefs,varb) {
 lp1 <- as.matrix(X1) %*% coefs
 lp0 <- as.matrix(X0) %*% coefs
 pred1 <- exp(lp1)/(1+exp(lp1))
 pred0 <- exp(lp0)/(1+exp(lp0))
 est <- mean(pred1-pred0)
 onc <- rep(1,length(coefs))
 p1mat <- pred1 %*% onc
 p0mat <- pred0 %*% onc
 onr <- rep(1,nrow(X1))
 onmat <- matrix(1,nrow=nrow(X1),ncol=ncol(X1))
 del <- t(X1*p1mat*(onmat-p1mat)-X0*p0mat*(onmat-p0mat)) %*% onr
 se <- as.numeric(sqrt(t(del) %*% varb %*% del)/nrow(X1))

 l95int <- est-qnorm(0.975,0,1)*se
 u95int <- est+qnorm(0.975,0,1)*se
 zstat <- est/se
 pvalue <- 2*(1-pnorm(abs(zstat),0,1))
 statinf <- c(est,se,l95int,u95int,pvalue)
 return(statinf)
}

#Function when a direct and indirect variables are manipulated
estpotoutint <- function(X1w,X0w,X10,X00,coefs,varb) {
 lp1w <- as.matrix(X1w) %*% coefs
 lp0w <- as.matrix(X0w) %*% coefs
 lp10 <- as.matrix(X10) %*% coefs
 lp00 <- as.matrix(X00) %*% coefs
 pred1w <- exp(lp1w)/(1+exp(lp1w))
 pred0w <- exp(lp0w)/(1+exp(lp0w))
 pred10 <- exp(lp10)/(1+exp(lp10))
 pred00 <- exp(lp00)/(1+exp(lp00))
 est <- mean(pred1w-pred0w-pred10+pred00)
 onc <- rep(1,length(coefs))
 p1wmat <- pred1w %*% onc
 p0wmat <- pred0w %*% onc
 p10mat <- pred10 %*% onc
 p00mat <- pred00 %*% onc
 onr <- rep(1,nrow(X1w))
 onmat <- matrix(1,nrow=nrow(X1w),ncol=ncol(X1w))
 del <- t(X1w*p1wmat*(onmat-p1wmat)-X0w*p0wmat*(onmat-p0wmat)-X10*p10mat*(onmat-p10mat)+X00*p00mat*(onmat-p00mat)) %*% onr
 se <- as.numeric(sqrt(t(del) %*% varb %*% del)/nrow(X1w))

 l95int <- est-qnorm(0.975,0,1)*se
 u95int <- est+qnorm(0.975,0,1)*se
 zstat <- est/se
 pvalue <- 2*(1-pnorm(abs(zstat),0,1))
 statinf <- c(est,se,l95int,u95int,pvalue)
 return(statinf)
}

estpotoutintint <- function(X1wt,X0wt,X1w0,X0w0,X10t,X00t,X100,X000,coefs,varb) {
 lp1wt <- as.matrix(X1wt) %*% coefs
 lp0wt <- as.matrix(X0wt) %*% coefs
 lp1w0 <- as.matrix(X1w0) %*% coefs
 lp0w0 <- as.matrix(X0w0) %*% coefs
 lp10t <- as.matrix(X10t) %*% coefs
 lp00t <- as.matrix(X00t) %*% coefs
 lp100 <- as.matrix(X100) %*% coefs
 lp000 <- as.matrix(X000) %*% coefs
 pred1wt <- exp(lp1wt)/(1+exp(lp1wt))
 pred0wt <- exp(lp0wt)/(1+exp(lp0wt))
 pred1w0 <- exp(lp1w0)/(1+exp(lp1w0))
 pred0w0 <- exp(lp0w0)/(1+exp(lp0w0))
 pred10t <- exp(lp10t)/(1+exp(lp10t))
 pred00t <- exp(lp00t)/(1+exp(lp00t))
 pred100 <- exp(lp100)/(1+exp(lp100))
 pred000 <- exp(lp000)/(1+exp(lp000))
 est <- mean(pred1wt-pred0wt-pred1w0+pred0w0-pred10t+pred00t+pred100-pred000)
 onc <- rep(1,length(coefs))
 p1wtmat <- pred1wt %*% onc
 p0wtmat <- pred0wt %*% onc
 p1w0mat <- pred1w0 %*% onc
 p0w0mat <- pred0w0 %*% onc
 p10tmat <- pred10t %*% onc
 p00tmat <- pred00t %*% onc
 p100mat <- pred100 %*% onc
 p000mat <- pred000 %*% onc
 onr <- rep(1,nrow(X1wt))
 onmat <- matrix(1,nrow=nrow(X1wt),ncol=ncol(X1wt))
 del <- t(X1wt*p1wtmat*(onmat-p1wtmat)-X0wt*p0wtmat*(onmat-p0wtmat)-X1w0*p1w0mat*(onmat-p1w0mat)+X0w0*p0w0mat*(onmat-p0w0mat)-X10t*p10tmat*(onmat-p10tmat)+X00t*p00tmat*(onmat-p00tmat)+X100*p100mat*(onmat-p100mat)-X000*p000mat*(onmat-p000mat)) %*% onr
 se <- as.numeric(sqrt(t(del) %*% varb %*% del)/nrow(X1wt))

 l95int <- est-qnorm(0.975,0,1)*se
 u95int <- est+qnorm(0.975,0,1)*se
 zstat <- est/se
 pvalue <- 2*(1-pnorm(abs(zstat),0,1))
 statinf <- c(est,se,l95int,u95int,pvalue)
 return(statinf)  
}

## Potential outcomes evaluation (Do not include n_stay_mds in the phase models) ##
## Condition on the mean of the potential outcomes distribution ##

mod_phase <- glmer(acp~phase+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+(1|HospitalID),family=binomial(link="logit"),nAGQ=2,data=data)
coefs <- fixef(mod_phase)
varb <- vcov(mod_phase)

#Estimate ADE and use Delta method to approximate standard errors
X1 <- datacov; X1$phase <- 1
X0 <- datacov; X0$phase <- 0
est_phase_ADE <- estpotout(X1,X0,coefs,varb)


mod_phasespill <- glmer(acp~phase+physWPost_strict_ext+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+(1|HospitalID),family=binomial(link="logit"),nAGQ=2,data=data)
coefs <- fixef(mod_phasespill)
varb <- vcov(mod_phasespill)
ncol <- ncol(datacov)
datacov <- data.frame(datacov[,1:2],spill=data$physWPost_strict_ext,datacov[,3:ncol])

#Estimate ADE (absent spillover) and use Delta method to approximate standard errors
#Estimate AIE (absent direct intervention and under a 10pp increase) and use Delta method to approximate standard errors
w <- 0.1*10 #Important: Need to emulate re-scaling of WPost_strict_ext to get corresponding estimate
X10 <- datacov; X10$phase <- 1; X10$spill <- 0;
X00 <- datacov; X00$phase <- 0; X00$spill <- 0;
X0w <- datacov; X0w$phase <- 0; X0w$spill <- w;
est_phasespill_ADE <- estpotout(X10,X00,coefs,varb)
est_phasespill_AIE <- estpotout(X0w,X00,coefs,varb)


mod_phasespillint <- glmer(acp~phase*physWPost_strict_ext+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+(1|HospitalID),family=binomial(link="logit"),nAGQ=2,data=data)
#In terms of BIC, it looks like both terms don't improve the model; thus dose interpolates phase
coefs <- fixef(mod_phasespillint)
varb <- vcov(mod_phasespillint)
datacov <- data.frame(datacov,intspill=datacov$phase*datacov$spill)

#Estimate ADE (absent spillover) and use Delta method to approximate standard errors
#Estimate AIE (absent direct effect and under a 10pp increase) and use Delta method to approximate standard errors
#Estimate ACE (with 10pp increase in peer-exposure) and use Delta method to approximate standard errors
#ACE(0.1) = ADE(0.1)-ADE(0) under interaction model
X1w <- datacov; X1w$phase <- 1; X1w$spill <- w; X1w$intspill <- X1w$phase*X1w$spill
X0w <- datacov; X0w$phase <- 0; X0w$spill <- w; X0w$intspill <- X0w$phase*X0w$spill
X10 <- datacov; X10$phase <- 1; X10$spill <- 0; X10$intspill <- X10$phase*X10$spill
X00 <- datacov; X00$phase <- 0; X00$spill <- 0; X00$intspill <- X00$phase*X00$spill
est_phasespillint_ADE <- estpotout(X10,X00,coefs,varb)
est_phasespillint_AIE <- estpotout(X0w,X00,coefs,varb)
est_phasespillint_ACE <- estpotoutint(X1w,X0w,X10,X00,coefs,varb)


mod_phasespillintret <- glmer(acp~phase*physWPost_strict_ext+phaseret+phaseexpret+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+(1|HospitalID),family=binomial(link="logit"),nAGQ=2,data=data)
#In terms of BIC, it looks like both terms don't improve the model; thus dose interpolates phase
coefs <- fixef(mod_phasespillintret)
varb <- vcov(mod_phasespillintret)
ncol <- ncol(datacov)
datacov <- data.frame(datacov[,1:3],phaseret=data$phaseret,phaseexpret=data$phaseexpret,datacov[,4:ncol])

#Estimate ADE (absent spillover) and use Delta method to approximate standard errors
#Estimate AIE (absent direct effect and under a 10pp increase) and use Delta method to approximate standard errors
#Estimate ACE (with 10pp increase in peer-exposure) and use Delta method to approximate standard errors
#ACE(0.1) = ADE(0.1)-ADE(0) under interaction model
t <- 90/90 #Emulate transformation used in estimation data to get effect corresponding to 90-day (1 quarter) change
X1w0 <- datacov; X1w0$phase <- 1; X1w0$spill <- w; X1w0$intspill <- X1w0$phase*X1w0$spill; X1w0$phaseret <- X1w0$phase*0; X1w0$phaseexpret <- X1w0$intspill*0
X0w0 <- datacov; X0w0$phase <- 0; X0w0$spill <- w; X0w0$intspill <- X0w0$phase*X0w0$spill; X0w0$phaseret <- X0w0$phase*0; X0w0$phaseexpret <- X0w0$intspill*0
X100 <- datacov; X100$phase <- 1; X100$spill <- 0; X100$intspill <- X100$phase*X100$spill; X100$phaseret <- X100$phase*0; X100$phaseexpret <- X100$intspill*0
X000 <- datacov; X000$phase <- 0; X000$spill <- 0; X000$intspill <- X000$phase*X000$spill; X000$phaseret <- X000$phase*0; X000$phaseexpret <- X000$intspill*0
X1wt <- datacov; X1wt$phase <- 1; X1wt$spill <- w; X1wt$intspill <- X1wt$phase*X1wt$spill; X1wt$phaseret <- X1wt$phase*t; X1wt$phaseexpret <- X1wt$intspill*t
X0wt <- datacov; X0wt$phase <- 0; X0wt$spill <- w; X0wt$intspill <- X0wt$phase*X0wt$spill; X0wt$phaseret <- X0wt$phase*t; X0wt$phaseexpret <- X0wt$intspill*t
X10t <- datacov; X10t$phase <- 1; X10t$spill <- 0; X10t$intspill <- X10t$phase*X10t$spill; X10t$phaseret <- X10t$phase*t; X10t$phaseexpret <- X10t$intspill*t
X00t <- datacov; X00t$phase <- 0; X00t$spill <- 0; X00t$intspill <- X00t$phase*X00t$spill; X00t$phaseret <- X00t$phase*t; X00t$phaseexpret <- X00t$intspill*t
est_phasespillintret_ADE <- estpotout(X100,X000,coefs,varb)
est_phasespillintret_AIE <- estpotout(X0w0,X000,coefs,varb)
est_phasespillintret_ACE <- estpotoutint(X1w0,X0w0,X100,X000,coefs,varb)
est_phasespillintret_ASE <- estpotoutint(X10t,X00t,X100,X000,coefs,varb)
est_phasespillintret_ARE <- estpotoutintint(X1wt,X0wt,X1w0,X0w0,X10t,X00t,X100,X000,coefs,varb)


#Dose-response models and time varying network case
datacov <- data.frame(factintercept,data[,c("n_intervened_mds","n_stay_mds")],factstep,factmonth,data$ctrialday,factregion,factage,factcovid,data[,c("cad_cd","dem_cd","heart_cd","diab_cd","lung_cd")],factccharl,data[,c("n_w2mds","covid_stays","Q2_Y20_Adj_ACP","Delta_ACP")],factcsq)
names(datacov) <- c("intercept","n_intervened_mds","n_stay_mds",paste("chosp_step",2:5,sep=""),paste("ctrialmonth",2:11,sep=""),"ctrialday",paste("cbregion",c("south","west"),sep=""),paste("age",c(75,85),sep=""),"ccovid_status","cad_cd","dem_cd","heart_cd","diab_cd","lung_cd",paste("ccharl_sc",1:5,sep=""),"n_w2mds","covid_stays","Q2_Y20_Adj_ACP","Delta_ACP","csq")

mod_dose <- glmer(acp~n_intervened_mds+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+(1|HospitalID),family=binomial(link="logit"),nAGQ=2,data=data)
coefs <- fixef(mod_dose)
varb <- vcov(mod_dose)

#Estimate ADE and use Delta method to approximate standard errors
basedose <- mean(data$n_intervened_mds,na.rm=TRUE)
X1 <- datacov; X1$n_intervened_mds <- basedose+0.5
X0 <- datacov; X0$n_intervened_mds <- basedose-0.5
est_dose_ADE <- estpotout(X1,X0,coefs,varb)


mod_dosespill <- glmer(acp~n_intervened_mds+physWPost_strict+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+(1|HospitalID),family=binomial(link="logit"),nAGQ=2,data=data)
coefs <- fixef(mod_dosespill)
varb <- vcov(mod_dosespill)
ncol <- ncol(datacov)
datacov <- data.frame(datacov[,1:2],spill=data$physWPost_strict,datacov[,3:ncol])

#Estimate ADE (absent spillover) and use Delta method to approximate standard errors
#Estimate AIE (absent direct intervention and under a 10pp increase) and use Delta method to approximate standard errors
w <- 1 #To emulate transformation applied to the dataset used for estimation
X10 <- datacov; X10$n_intervened_mds <- basedose+0.5; X10$spill <- 0;
X00 <- datacov; X00$n_intervened_mds <- basedose-0.5; X00$spill <- 0;
X0w <- datacov; X0w$n_intervened_mds <- basedose-0.5; X0w$spill <- w;
est_dosespill_ADE <- estpotout(X10,X00,coefs,varb)
est_dosespill_AIE <- estpotout(X0w,X00,coefs,varb)


mod_dosespillint <- glmer(acp~n_intervened_mds*physWPost_strict+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+(1|HospitalID),family=binomial(link="logit"),nAGQ=2,data=data)
coefs <- fixef(mod_dosespillint)
varb <- vcov(mod_dosespillint)
datacov <- data.frame(datacov,intspill=datacov$n_intervened_mds*datacov$spill)

#Estimate ADE (absent spillover) and use Delta method to approximate standard errors
#Estimate AIE (absent direct effect and under a 10pp increase) and use Delta method to approximate standard errors
#Estimate ACE (with 10pp increase in peer-exposure) and use Delta method to approximate standard errors
#ACE(0.1) = ADE(0.1)-ADE(0) under interaction model
X1w <- datacov; X1w$n_intervened_mds <- basedose+0.5; X1w$spill <- w; X1w$intspill <- X1w$n_intervened_mds*X1w$spill
X0w <- datacov; X0w$n_intervened_mds <- basedose-0.5; X0w$spill <- w; X0w$intspill <- X0w$n_intervened_mds*X0w$spill
X10 <- datacov; X10$n_intervened_mds <- basedose+0.5; X10$spill <- 0; X10$intspill <- X10$n_intervened_mds*X10$spill
X00 <- datacov; X00$n_intervened_mds <- basedose-0.5; X00$spill <- 0; X00$intspill <- X00$n_intervened_mds*X00$spill
est_dosespillint_ADE <- estpotout(X10,X00,coefs,varb)
est_dosespillint_AIE <- estpotout(X0w,X00,coefs,varb)
est_dosespillint_ACE <- estpotoutint(X1w,X0w,X10,X00,coefs,varb)


mod_dosespillintret <- glmer(acp~n_intervened_mds*physWPost_strict+n_intret+n_intexpret+n_stay_mds+chosp_step+ctrialmonth+ctrialday+cbregion+cageg+ccovid_status+cad_cd+dem_cd+heart_cd+diab_cd+lung_cd+ccharl_sc+n_w2mds+covid_stays+Q2_Y20_Adj_ACP+Delta_ACP+csq+(1|HospitalID),family=binomial(link="logit"),nAGQ=2,data=data)
coefs <- fixef(mod_dosespillintret)
varb <- vcov(mod_dosespillintret)
ncol <- ncol(datacov)
datacov <- data.frame(datacov[,1:3],n_ret=data$n_intret,n_expret=data$n_intexpret,datacov[,4:ncol])

#Estimate ADE (absent spillover) and use Delta method to approximate standard errors
#Estimate AIE (absent direct effect and under a 10pp increase) and use Delta method to approximate standard errors
#Estimate ACE (with 10pp increase in peer-exposure) and use Delta method to approximate standard errors
#ACE(0.1) = ADE(0.1)-ADE(0) under interaction model
t <- 1
X1w0 <- datacov; X1w0$n_intervened_mds <- basedose+0.5; X1w0$spill <- w; X1w0$intspill <- X1w0$n_intervened_mds*X1w0$spill; X1w0$n_ret <- X1w0$n_intervened_mds*0; X1w0$n_expret <- X1w0$intspill*0
X0w0 <- datacov; X0w0$n_intervened_mds <- basedose-0.5; X0w0$spill <- w; X0w0$intspill <- X0w0$n_intervened_mds*X0w0$spill; X0w0$n_ret <- X0w0$n_intervened_mds*0; X0w0$n_expret <- X0w0$intspill*0
X100 <- datacov; X100$n_intervened_mds <- basedose+0.5; X100$spill <- 0; X100$intspill <- X100$n_intervened_mds*X100$spill; X100$n_ret <- X100$n_intervened_mds*0; X100$n_expret <- X100$intspill*0
X000 <- datacov; X000$n_intervened_mds <- basedose-0.5; X000$spill <- 0; X000$intspill <- X000$n_intervened_mds*X000$spill; X000$n_ret <- X000$n_intervened_mds*0; X000$n_expret <- X000$intspill*0
X1wt <- datacov; X1wt$n_intervened_mds <- basedose+0.5; X1wt$spill <- w; X1wt$intspill <- X1wt$n_intervened_mds*X1wt$spill; X1wt$n_ret <- X1wt$n_intervened_mds*t; X1wt$n_expret <- X1wt$intspill*t
X0wt <- datacov; X0wt$n_intervened_mds <- basedose-0.5; X0wt$spill <- w; X0wt$intspill <- X0wt$n_intervened_mds*X0wt$spill; X0wt$n_ret <- X0wt$n_intervened_mds*t; X0wt$n_expret <- X0wt$intspill*t
X10t <- datacov; X10t$n_intervened_mds <- basedose+0.5; X10t$spill <- 0; X10t$intspill <- X10t$n_intervened_mds*X10t$spill; X10t$n_ret <- X10t$n_intervened_mds*t; X10t$n_expret <- X10t$intspill*t
X00t <- datacov; X00t$n_intervened_mds <- basedose-0.5; X00t$spill <- 0; X00t$intspill <- X00t$n_intervened_mds*X00t$spill; X00t$n_ret <- X00t$n_intervened_mds*t; X00t$n_expret <- X00t$intspill*t
est_dosespillintret_ADE <- estpotout(X100,X000,coefs,varb)
est_dosespillintret_AIE <- estpotout(X0w0,X000,coefs,varb)
est_dosespillintret_ACE <- estpotoutint(X1w0,X0w0,X100,X000,coefs,varb)
est_dosespillintret_ASE <- estpotoutint(X10t,X00t,X100,X000,coefs,varb)
est_dosespillintret_ARE <- estpotoutintint(X1wt,X0wt,X1w0,X0w0,X10t,X00t,X100,X000,coefs,varb)

mod_phase_res<-format_model_output_logistic(mod_phase,variable_mapping = variable_mapping)
write.csv(mod_phase_res,"causal_spillover_phase_tinv.csv",row.names=F)

mod_phasespill_res<-format_model_output_logistic(mod_phasespill,variable_mapping = variable_mapping)
write.csv(mod_phasespill_res,"causal_spillover_phasespill_tinv.csv",row.names=F)

mod_phasespillint_res<-format_model_output_logistic(mod_phasespillint,variable_mapping = variable_mapping)
write.csv(mod_phasespillint_res,"causal_spillover_phasespillint_tinv.csv",row.names=F)

mod_phasespillintret_res<-format_model_output_logistic(mod_phasespillintret,variable_mapping = variable_mapping)
write.csv(mod_phasespillintret_res,"causal_spillover_phasespillintret_tinv.csv",row.names=F)

mod_dose_res<-format_model_output_logistic(mod_dose,variable_mapping = variable_mapping)
write.csv(mod_dose_res,"causal_spillover_dose_tinv.csv",row.names=F)

mod_dosespill_res<-format_model_output_logistic(mod_dosespill,variable_mapping = variable_mapping)
write.csv(mod_dosespill_res,"causal_spillover_dosespill_tinv.csv",row.names=F)

mod_dosespillint_res<-format_model_output_logistic(mod_dosespillint,variable_mapping = variable_mapping)
write.csv(mod_dosespillint_res,"causal_spillover_dosespillint_tinv.csv",row.names=F)

mod_dosespillintret_res<-format_model_output_logistic(mod_dosespillintret,variable_mapping = variable_mapping)
write.csv(mod_dosespillintret_res,"causal_spillover_dosespillintret_tinv.csv",row.names=F)

## Output estimates of potential outcomes and associated inferential quantities ##

outphasetinv <- matrix(c(est_phase_ADE,est_phasespill_ADE,est_phasespill_AIE,est_phasespillint_ADE,est_phasespillint_AIE,est_phasespillint_ACE,est_phasespillintret_ADE,est_phasespillintret_AIE,est_phasespillintret_ACE,est_phasespillintret_ASE,est_phasespillintret_ARE),ncol=5,byrow=T)
outphasetinv <- data.frame(outphasetinv)
names(outphasetinv) <- c("estimate","SE","Low95","Up95","p-value")
write.csv(outphasetinv,"causal_spillover_phase_tinv_potout.csv",row.names=F)

outdosetinv <- matrix(c(est_dose_ADE,est_dosespill_ADE,est_dosespill_AIE,est_dosespillint_ADE,est_dosespillint_AIE,est_dosespillint_ACE,est_dosespillintret_ADE,est_dosespillintret_AIE,est_dosespillintret_ACE,est_dosespillintret_ASE,est_dosespillintret_ARE),ncol=5,byrow=T)
outdosetinv <- data.frame(outdosetinv)
names(outdosetinv) <- c("estimate","SE","Low95","Up95","p-value")
write.csv(outdosetinv,"causal_spillover_dose_tinv_potout.csv",row.names=F)
```
